---
title: "RevigoR"
author: "Felix GM Ernst"
date: "`r Sys.Date()`"
output: 
    BiocStyle::html_document:
        toc: true
        toc_float: true
        df_print: paged
vignette: >
  %\VignetteIndexEntry{RevigoR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: references.bib 
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

Revigo [@SupekF.2011] is a web service ([http://revigo.irb.hr/](http://revigo.irb.hr/)) for visualizing lists of gene ontology (GO) terms and their relation to each others. As input a list of gene ontology terms and optionally associated p-values are accepted. To access the information directly from a R session `RevigoR` can be used.

# Get Revigo data

Their are several option to get the Revigo results. It largely depends, how the GO terms are stored. The simplest option is a data.frame with two columns for GO terms in the format `GO:XXXXXX` and their associated p-values. 

```{r revigor_simple}
data("rdinput", package = "RevigoR")
rdinput

rd <- getRevigo(rdinput)
rd
```

The results are saved as a `RevigoData` object, which is basically a `SimpleList` with a fixed length of two (table and treemap keays)

```{r revigor_data}
rd
all(getTableData(rd) == rd[["table"]], na.rm = TRUE)
```

For commonly used GO objects such as `DAVIDFunctionalAnnotationChart` from the `RDAVIDWebService`. Since a chart can hold data different GO categories, a category has to be chosen for subsetting.

```{r revigor_david}
data("chart", package = "RevigoR")
chart
# also 
rd <- getRevigo(chart,
                goCategory = "GOTERM_BP_DIRECT")
rd
```


# Plot Revigo type figures

Results from Revigo are usually plotted as a scatter plot or treemap as done on the web site

```{r revigor_scatter, eval=FALSE}
plotRevigoScatter(rd)
```

```{r plot1, fig.cap="Revigo scatter plot", echo=FALSE}
plotRevigoScatter(rd)
```

```{r revigor_treemap, eval=FALSE}
plotRevigoTreemap(rd)
```

```{r plot2, fig.cap="Revigo treemap plot", echo=FALSE}
plotRevigoTreemap(rd)
```

# Sessioninfo

```{r build_info}
sessionInfo()
```

# References
